
\subsection{Product perspective}
The recollection of the data will be carried out by the mobile devices of the users, upon installation of the application of \companyName{}. Before the recollection of data takes place, the users have to register to the system and give their approval.

To enable the analysis of the data to the clients, \companyName{} provides centralised tools by means of an online dashboard and an API endpoint. The latter is intended to facilitate the integration of \companyName{} platform with client's ones.

The payment of the clients for accessing the data is handle by a third party system and integrated in \companyName{}. The request of ambulances is performed by a third party service, presumably an public service offered by the government.

\begin{figure}[H]

\centering
\begin{tikzpicture}[node distance=3cm]

\node (server) [cuadrado] {Server};
\node (dashboard) [cuadrado, right =3cm of server] {Dashboard};
\node (external) [cuadrado, below of=dashboard] {Client system};
\node (mobile) [cuadrado, left =3cm of server] {Mobile};
\node (smartwatch) [cuadrado, below of=mobile] {Smartwatch};

\node (payment) [cuadrado, above of=dashboard] {Payment system};
\node (sos) [cuadrado, above of=mobile] {Emergence system};

\draw[dashed, ->] (mobile) -- (server) node [midway, above] {\footnotesize \companyName{} API};
\draw[dashed, ->] (smartwatch) -- (mobile);
\draw[dashed, <->] (server) -- (dashboard) node [midway, above] {\footnotesize \companyName{} API};
\draw[solid, <->] (server) |- (external) node [midway, below] {\footnotesize \companyName{} API};
\draw[solid, <->] ([xshift=2cm]server) |- (payment) node [midway, right, yshift=.3cm] {\footnotesize Payment API};
\draw[solid, <->] ([xshift=-2cm]server) |- (sos) node [midway, left, yshift=.3cm] {\footnotesize Emergence API};
\end{tikzpicture}
    \caption{Overview of the system}
    \label{fig:overview-system}
\end{figure}

%The recollected data is organised in parameters. Each parameter corresponds with the data collected from a type of sensor of the user device. 

An overview of the system is shown in figure \ref{fig:overview-system}. The dashed lines represents connections between elements of the \companyName{} system while the solid ones corresponds to outside ones. These connections are discussed more profoundly in sections \ref{sec:dependencies} and \ref{sec:interfaces}.

The components connected by dashed lines are internal of the system and therefore no requirements will be impose on these interfaces. However, stating the general architecture of the solution removes vagueness and allows the requirements to be specified in a more concise way.


%Privacy issues may arise. The recollection of private data is subject to a strong regulation in the European Union and therefore, mechanism to enforce a fair usage of the platform may be in place.

%As a general rule, the querying of information should never return data that enable the differentiation of individuals. Returning a few records for a query may expose the individuals behind that data, and therefore is not allowed.

%The only option for a client to access to individual data is to request permission to the specific user. This will be done by mean of the system. The client should provide the unique identifier of the user, for example the codice fiscale. 

\subsection{Product functions}
The main functions of the product are detailed below. The requirements stated later pursue the implementation of these functions.

\subsubsection{Recollection of users' data}
The related goals are \goalref{gl:registration}, \goalref{gl:recollect}, \goalref{gl:how-recollect} and \goalref{gl:intervals}.

The recollection of the users' data will be carried out by the users' devices\footnote{i.e. smartwatch and smartphone} and stored by the server of \companyName{}. The data will be grouped by parameters. The parameters are defined in section \ref{sec:parameters-appendix}.

An important distinction has to be made between fixed parameters and temporary ones. The former includes data that not changes, like the birth of date, codice fiscale, name, residence and so on. The latter will be recollected at a fixed interval of time and stored with a time-stamp associated with them. Location and heart rate are in this group.

These temporary parameters are not limited to the information recollected by the sensors of the users' devices. Some parameters, as for example the weight, may need the manual collaboration of the user to be recollected. This may be accomplished by promping the user to introduce the information in the application by himself. These kind of parameters will be called manual parameters.

This function is the cornerstone of the entire system, as the rest of the functionalities are devoted to consuming the recollected data. 

\subsubsection{Querying data}
The related goals are \goalref{gl:time}, \goalref{gl:query}, \goalref{gl:individuals}, \goalref{gl:privacy} and \goalref{gl:privacy}.

The data stored in the server will be available to the clients. The system should allow clients to build a query based on the available parameters. This query will return a data batch\footnote{See data batch definition on \ref{sec:definitions}}.

The clients will be provided with two ways of accessing the data. The first one will be by mean of an online dashboard\footnote{i.e. a web page} and an API.

The latter is intended to erase the interconnection between the system of the client and the \companyName{} one. Because of this, the API functionalities will be limited to querying data.

No matter what way the client use, two access of the data should be distinguish:

\begin{itemize}
    \item \textbf{Anonymous query (Group search)}: Query that return a data batch with enough entries to be considered anonymous, i.e. not individuals can be distinguish.
    
    \item \textbf{Individual query}: Query by an identifier related univocally to an user. The client must elicit the permission of the user before getting the data. 
\end{itemize}

This distinction is tightly related to goals \goalref{gl:individuals} and \goalref{gl:privacy}.
The related goal is \goalref{gl:emergency}.

The charge to the clients for the access will be by means of a subscription.

\subsubsection{Ambulance service (AutomatedSOS)}
The related goal is \goalref{gl:emergency}.

AutomatedSOS is an extra service offered to the users. The system will monitor a set of parameters further detailed in \ref{sect:requirements}. When some of these parameters goes out of a threshold predefined by \companyName{}, an alarm will be raised to the Emergency System, attaching the location of the user, the phone number and the phone number of a family member.

The aforementioned alarm will be communicated to the Emergency System by electronic means, using an API offered by the Emergency System.

\subsection{User characteristics}

There are three different types of actors in the system. Their definitions can be found in \ref{sec:definitions}. Through these sections, each type will be analysed and an attempt of characterising them based on demographics will be made.

\subsubsection{Users}
The potential users can be segmented by age:
\begin{itemize}
    \item \textbf{Generation Z}: Born between 2000's and onwards. 95\% of persons in this age interval have a smartphone. They prefer the smartphone over the laptop \cite{smartphones-z}. They are comfortable sharing personal data in order to get a more personalised experience \cite{privacy-z}.
    \item \textbf{Millennials}:  Born between 1980 and 2000's, the so-called \textit{digital natives} are very confident in their abilities with digital interfaces and are used to fast-paced interactions.\cite{digital-natives}. They read less than the average user \cite{digital-natives}, which leads to a rapid acceptation of the terms of usage of any application.
    \item \textbf{Generation X}: Born between 1980 and 1960. According to \cite{generation-x}, 85\% of \textit{Gen Xers} owns a smartphone, which makes this generation a good segment for \companyName{} product. They are generally influenced by convenient purposes and will keep aside digital products \cite{convenience-generation-x} if they do not feel comfortable with them.
    
    \item \textbf{Baby boomers}: Born between 1946 and 1964. The market segment of \textit{Boomers} is very interesting since they have a great acquisition power. However, the penetration of fitness tracking devices are very scarce in this demographic interval. In fact, \textit{Boomers} usually found difficulties in using the health monitor devices \cite{boomers-fitness}.  
\end{itemize}

With these segments in mind, \companyName{} system will be target to the three first segments. Specially taking into account that Generation Z and Millennials are not concerned about the lack of privacy. Generation X users have a great purchase power, but will be more reticent to the acceptation of the terms of usage. 

AutomatedSOS will be oriented to Baby Boomers. Since they usually found difficulties in the usage of the fitness tracking devices, the application should be simple and concise. 
\subsection{Clients}
Clients are assumed to be companies interested in offering a better service through the use of data. The main sectors in which the \companyName{} system shall focus are:
\begin{itemize}
    \item \textbf{Insurance:} They will be able to present to the users insurances more adapted to them (for example thanks to their location if they make many trips they will be able to offer them insurances more dedicated to it) as well as discounts by the state of health that the users may present. 
    
    It is also presented as an advantage for the insurer since thanks to the different data they can calculate the profitability that a user presents to them.

    \item \textbf{Marketing:} They allow companies to provide more personalised marketing and advertising services for each user thanks to the lifestyle data of each one.
    
    \item \textbf{Banks:} They can offer better offers in mortgages or loans to the users thanks to the different data that \companyName{} offers since they are able to know the state of health and the type of life that their clients have.
    
    Thanks to \companyName{}, the bank has an advantage since it can calculate the situation in which its clients will find themselves during the repayment of the loan or mortgage.
    \item \textbf{Wellness and health applications:} They can use \companyName{}'s data for a better control of their clients and thus present a more personalised information to each user.
\end{itemize}


\subsection{Assumptions, dependencies and constrains}

\subsubsection{Assumptions}

\begin{table}[H]
  \centering
    \begin{adjustbox}{max width=\textwidth}
  \begin{tabular}{cp{14cm}}
    \toprule
    \textbf{ID} & \textbf{Description}\\
    \midrule
    
    \assumlabel{as:gps} &
    \begin{tabular}{@{}p{14cm}@{}}
    Users' mobile have GPS sensor.
    \end{tabular}\\
    \hline 
    
    \assumlabel{as:smarthwatch} &
    \begin{tabular}{@{}p{14cm}@{}}
    Users' smarthwatch have an accurate hearth rate sensor.
    \end{tabular}\\
    \hline
    
    \assumlabel{as:sensor-permission} &
    \begin{tabular}{@{}p{14cm}@{}}
    Users eventually accepts Android Permission Request of the necessary sensors.
    \end{tabular}\\
    \hline
    
    \assumlabel{as:answers} &
    \begin{tabular}{@{}p{14cm}@{}}
    Users will answer the questions prompted by the application with reliable information.
    \end{tabular}\\
    \hline
    
    \assumlabel{as:background} &
    \begin{tabular}{@{}p{14cm}@{}}
    Users will grant permissions to the application to work in the background.
    \end{tabular}\\
    \hline
    
    \assumlabel{as:internet} &
    \begin{tabular}{@{}p{14cm}@{}}
    Users's devices will have internet connection when the application will send the data to the server.
    \end{tabular}\\
    \hline
    
    \assumlabel{as:use-smartwatch} &
    \begin{tabular}{@{}p{14cm}@{}}
    The user that owns the smarthphone in which the application is installed is the same user which wears the smarthwatch.
    \end{tabular}\\
    \hline
    
    \assumlabel{as:real-data} &
    \begin{tabular}{@{}p{14cm}@{}}
    The users provides veridic data when registering.
    \end{tabular}\\
    \hline
    
    \assumlabel{as:clients-pay} &
    \begin{tabular}{@{}p{14cm}@{}}
    Clients provides a card account with enough funds.
    \end{tabular}\\
    \hline
    
    \assumlabel{as:emergency} &
    \begin{tabular}{@{}p{14cm}@{}}
    The emergency system API process a request in less than one second. 
    \end{tabular}\\
    \hline
    
    \assumlabel{as:location} &
    \begin{tabular}{@{}p{14cm}@{}}
    The user do not move more than 20 meters between the call to the emergency API an the arrival of the ambulance.
    \end{tabular}\\
    
    \bottomrule
  \end{tabular}
  \end{adjustbox}
  \caption{Domain assumptions}
  \label{table:assumptions}
\end{table}



\subsubsection{Dependencies}\label{sec:dependencies}
\companyName{} system relies in two external systems to perform several tasks:
\begin{itemize}
    \item \textbf{Stripe}: Payment system that allows \companyName{} system to charge the clients a monthly fee for the access to the data. Stripe stands out over the competitors because its API, which is recognized as one of the best in the business \cite{stripe}.
    \item \textbf{Emergency system}: To offer AutomatedSOS, \companyName{} system needs a programmatic way to reach the emergency institutions. Therefore, an API is needed to rise an alarm when required.
\end{itemize}
Tables \ref{table:api-emergency} and \ref{table:api-pay} contains the format and endpoints needed for the proper functioning of \companyName{} product.
\begin{table}[H]
  \centering
    \begin{adjustbox}{max width=\textwidth}
  \begin{tabular}{cccp{4cm}p{2cm}p{9cm}}
    \toprule
    \textbf{ID} & \textbf{Method} & \textbf{URL} & \textbf{Parameters} & \textbf{Return} & \textbf{Description}\\
    \midrule
    
    \silabel{si:emergency-alarm} & POST &
    /ambulance
    &
    \begin{tabular}{@{}p{4cm}@{}}
    location, phone number, phone number of a family member, triggered parameter 
    \end{tabular} &
    \begin{tabular}{@{}p{2cm}@{}}
     estimated time 
    \end{tabular} &
    \begin{tabular}{@{}p{9cm}@{}}
    Call when an emergency service is needed, the important data of the customer is send to the Emergency system
    \end{tabular} \\
    
    \bottomrule
  \end{tabular}
  \end{adjustbox}
  \caption{Software interfaces of Emergency API}
  \label{table:api-emergency}
\end{table}

\begin{table}[H]
  \centering
    \begin{adjustbox}{max width=\textwidth}
  \begin{tabular}{cccp{4cm}p{2cm}p{9cm}}
    \toprule
    \textbf{ID} & \textbf{Method} & \textbf{URL} & \textbf{Parameters} & \textbf{Return} & \textbf{Description} \\
    \midrule
    
    \silabel{si:pay-create-card} & POST &
    /v1/tokens
    &
    \begin{tabular}{@{}p{4cm}@{}}
    Card Nº, Card expiration, CVC
    \end{tabular} &
    \begin{tabular}{@{}p{2cm}@{}}
    Card ID
    \end{tabular} &
    \begin{tabular}{@{}p{9cm}@{}}
    Register a card to be used in \siref{si:pay-create-customer}. One time use.
    \end{tabular} \\
    \hline
    
    \silabel{si:pay-create-customer} & POST &
    /v1/customer
    &
    \begin{tabular}{@{}p{4cm}@{}}
    Card ID, email
    \end{tabular} &
    \begin{tabular}{@{}p{2cm}@{}}
    Customer ID
    \end{tabular} &
    \begin{tabular}{@{}p{9cm}@{}}
    Register a client in the payment system, returns the ID that identifies the client in the payment system.
    \end{tabular} \\
    \hline
    
    \silabel{si:pay-subscribe-customer} & POST &
    /v1/subscriptions
    &
    \begin{tabular}{@{}p{4cm}@{}}
    Customer ID, Plan ID
    \end{tabular} &
    \begin{tabular}{@{}p{2cm}@{}}
    Subscription ID
    \end{tabular} &
    \begin{tabular}{@{}p{9cm}@{}}
    Starts charging the client the amont indicated by the Plan ID
    \end{tabular} \\
    \hline
    
    \silabel{si:pay-cancel-customer} & DELETE &
    /v1/subscriptions
    &
    \begin{tabular}{@{}p{4cm}@{}}
    Subscription ID
    \end{tabular} &
    \begin{tabular}{@{}p{2cm}@{}}
    Subscription ID
    \end{tabular} &
    \begin{tabular}{@{}p{9cm}@{}}
    Register a client in the payment system, returns the ID that identifies the client in the payment system.
    \end{tabular} \\
    
    \bottomrule
  \end{tabular}
  \end{adjustbox}
  \caption{Software interfaces of Payment API}
  \label{table:api-pay}
\end{table}

The official documentation of Stripe can be consulted in \url{https://stripe.com/docs}.


\subsubsection{Constraints}
\label{sec:constraints}
To ensure the proper work of \companyName{} system, several constraints will be in place. The constraints will be formulated upon the different components of the system stated in figure \ref{fig:overview-system}.

\begin{table}[H]
  \centering
    \begin{adjustbox}{max width=\textwidth}
  \begin{tabular}{cccp{10cm}}
    \toprule
    \textbf{ID} & \textbf{Element} & \textbf{Value} &\textbf{Motivation} \\
    \midrule
    
    \conslabel{cons:android-version} & 
    Operating system
    & Android 7.0 to 9.0 &
    \begin{tabular}{@{}p{10cm}@{}}
    These versions agglutinate the 54\% of the Android users \cite{versions-android}. The versions left behind are not supported anymore by Google.
    \end{tabular} \\
    \hline 
    
    \conslabel{cons:android-ram} & 
    Minimum RAM 
    & 1GB &
    \begin{tabular}{@{}p{10cm}@{}}
    The application will not be very demanding in terms of RAM. However, the proper functioning is only ensure to devices with 1GB of RAM or more.
    \end{tabular} \\
    \hline 
    
    \conslabel{cons:android-space} & 
    Minimum free space 
    & 50MB &
    \begin{tabular}{@{}p{10cm}@{}}
    The application will occupy 50MB or less in the internal storage of the users' devices.
    \end{tabular} \\
    \hline 
    
    \conslabel{cons:android-orientation} & 
    Orientation
    & Vertical &
    \begin{tabular}{@{}p{10cm}@{}}
    The application will not adapt to a change in device orientation. Will be always in vertical.
    \end{tabular} \\
    \hline
    
    \conslabel{cons:android-background} & 
    Background activity
    & Yes &
    \begin{tabular}{@{}p{10cm}@{}}
    The application will only work properly if background activity is allowed by the users' devices. 
    \end{tabular} \\
    \hline
    
    \conslabel{cons:android-orientation} &
    Smartwatch
    & AndroidWear &
    \begin{tabular}{@{}p{10cm}@{}}
    The application will only recollect health status data if the smartwatch paired with the user device is powered by AndroidWear.
    \end{tabular} \\
    \bottomrule
    
  \end{tabular}
  \end{adjustbox}
  \caption{Mobile application}
  \label{table:mobile-constraints}
\end{table}

\begin{table}[H]
  \centering
    \begin{adjustbox}{max width=\textwidth}
  \begin{tabular}{cccp{10cm}}
    \toprule
    \textbf{ID} & \textbf{Element} & \textbf{Value} &\textbf{Motivation} \\
    \midrule
    
    \conslabel{cons:server-os} & 
    Operating system
    & Ubuntu Server 16.04 &
    \begin{tabular}{@{}p{10cm}@{}}
    The proper functioning of the server will be only ensure in Ubuntu Server 16.04. Other operating systems may be consider upon approval of JJ Software.
    \end{tabular} \\
    \hline 
    
    \conslabel{cons:server-ram} & 
    Minimum RAM
    & 32 GB &
    \begin{tabular}{@{}p{10cm}@{}}
    The server will need to withstand an important workload, therefore 32GB of RAM is needed.
    \end{tabular} \\
    \hline 
    
    \conslabel{cons:server-space} & 
    Minimum disk space
    & 200 GB &
    \begin{tabular}{@{}p{10cm}@{}}
    This space will be needed to store all the data of the users in a secure way.
    \end{tabular} \\
    \hline 
    
    \conslabel{cons:server-bw} & 
    Minimum bandwidth
    & 500 Mb/s &
    \begin{tabular}{@{}p{10cm}@{}}
    To offer a good throughput, 500 Mb/s are needed to coupe with the users and clients request.
    \end{tabular} \\
    \bottomrule
    
  \end{tabular}
  \end{adjustbox}
  \caption{Server}
  \label{table:server-constraints}
\end{table}

\begin{table}[H]
  \centering
    \begin{adjustbox}{max width=\textwidth}
  \begin{tabular}{ccp{4cm}p{8cm}}
    \toprule
    \textbf{ID} & \textbf{Element} & \textbf{Value} &\textbf{Motivation} \\
    \midrule
    
    \conslabel{cons:browsers} & 
    Supported browsers &
    \begin{tabular}{@{}p{4cm}@{}}
    Safari 10, Firefox 50, Chrome 60, IE 11, Edge 10, Opera
    \end{tabular} &
    \begin{tabular}{@{}p{8cm}@{}}
    The dashboard will properly work in all modern browsers, from the versions stated on the left and above.
    \end{tabular} \\
    \bottomrule
    
    
    \conslabel{cons:display} & 
    Minimum display &
    \begin{tabular}{@{}p{4cm}@{}}
    1024px x 784px
    \end{tabular} &
    \begin{tabular}{@{}p{8cm}@{}}
    This is the minimun display resolution in which the dashboard will look as in the mockups.
    \end{tabular} \\
    \bottomrule
    
  \end{tabular}
  \end{adjustbox}
  \caption{Clients' Dashboard}
  \label{table:dashboard-constraints}
\end{table}